\documentclass[12pt, a4paper]{article}

% --- PACKAGES ---
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{pmboxdraw}
\usepackage{newunicodechar}
\usepackage[english]{babel}
\usepackage{helvet}               % Helvetica for a clean, tech look
\renewcommand{\familydefault}{\sfdefault}
\usepackage{setspace}             % For line spacing
\usepackage[top=2.5cm, bottom=2.5cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage{amsmath, amssymb, amsfonts}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{listings}             % For code snippets
\usepackage{tcolorbox}            % For highlighted boxes
\usepackage{tabularx}             % For auto-wrapping tables
\usepackage{array}                % For extra table column formatting
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{mathtools}
\usepackage{pdfpages}             % For including other PDFs if needed

% --- Define Left-Aligned X Column for Tables ---
\newcolumntype{L}{>{\raggedright\arraybackslash}X}

% --- URL BREAKING ---
\usepackage{xurl}
\usepackage{hyperref}

% --- CONFIGURATION ---
\onehalfspacing                   % 1.5 Line Spacing for readability and length

% --- HEADER HEIGHT ---
\setlength{\headheight}{15pt}

\definecolor{janusblue}{RGB}{0, 51, 102}
\definecolor{accentgold}{RGB}{204, 153, 51}
\definecolor{warnred}{RGB}{153, 0, 0}
\definecolor{forwardblue}{RGB}{51, 102, 153}
\definecolor{backwardblue}{RGB}{30, 60, 114}
\definecolor{neurocolor}{RGB}{102, 51, 153}
\definecolor{rustcolor}{RGB}{206, 92, 0}
\definecolor{codegray}{RGB}{245, 245, 245}

% --- UNICODE CHARACTER DECLARATIONS ---
\newunicodechar{▼}{\ensuremath{\blacktriangledown}}
\newunicodechar{→}{\ensuremath{\rightarrow}}
\newunicodechar{←}{\ensuremath{\leftarrow}}
\newunicodechar{↔}{\ensuremath{\leftrightarrow}}
\newunicodechar{⇒}{\ensuremath{\Rightarrow}}
\newunicodechar{…}{\ldots}
\newunicodechar{≥}{\ensuremath{\geq}}
\newunicodechar{≤}{\ensuremath{\leq}}
\newunicodechar{≠}{\ensuremath{\neq}}
\newunicodechar{∈}{\ensuremath{\in}}
\newunicodechar{∀}{\ensuremath{\forall}}
\newunicodechar{∃}{\ensuremath{\exists}}
\newunicodechar{∧}{\ensuremath{\wedge}}
\newunicodechar{∨}{\ensuremath{\vee}}
\newunicodechar{¬}{\ensuremath{\neg}}
\newunicodechar{⊕}{\ensuremath{\oplus}}
\newunicodechar{⊗}{\ensuremath{\otimes}}
\newunicodechar{∑}{\ensuremath{\sum}}
\newunicodechar{∏}{\ensuremath{\prod}}
\newunicodechar{∫}{\ensuremath{\int}}
\newunicodechar{∂}{\ensuremath{\partial}}
\newunicodechar{∇}{\ensuremath{\nabla}}
\newunicodechar{α}{\ensuremath{\alpha}}
\newunicodechar{β}{\ensuremath{\beta}}
\newunicodechar{γ}{\ensuremath{\gamma}}
\newunicodechar{δ}{\ensuremath{\delta}}
\newunicodechar{ε}{\ensuremath{\epsilon}}
\newunicodechar{θ}{\ensuremath{\theta}}
\newunicodechar{λ}{\ensuremath{\lambda}}
\newunicodechar{μ}{\ensuremath{\mu}}
\newunicodechar{π}{\ensuremath{\pi}}
\newunicodechar{σ}{\ensuremath{\sigma}}
\newunicodechar{τ}{\ensuremath{\tau}}
\newunicodechar{φ}{\ensuremath{\phi}}
\newunicodechar{ω}{\ensuremath{\omega}}
\newunicodechar{Δ}{\ensuremath{\Delta}}
\newunicodechar{Θ}{\ensuremath{\Theta}}
\newunicodechar{Σ}{\ensuremath{\Sigma}}
\newunicodechar{Φ}{\ensuremath{\Phi}}
\newunicodechar{Ω}{\ensuremath{\Omega}}
\newunicodechar{℘}{\ensuremath{\wp}}
\newunicodechar{ℝ}{\ensuremath{\mathbb{R}}}
\newunicodechar{ℕ}{\ensuremath{\mathbb{N}}}
\newunicodechar{ℤ}{\ensuremath{\mathbb{Z}}}
\newunicodechar{⟨}{\ensuremath{\langle}}
\newunicodechar{⟩}{\ensuremath{\rangle}}

% --- HYPERLINK CONFIGURATION ---
\hypersetup{
    colorlinks=true,
    linkcolor=janusblue,
    filecolor=janusblue,
    urlcolor=janusblue,
    citecolor=janusblue,
    pdftitle={Project JANUS - Complete Technical Documentation},
    pdfauthor={Jordan Smith},
    pdfsubject={Neuromorphic Trading Intelligence},
    pdfkeywords={algorithmic trading, neuromorphic computing, machine learning, Rust}
}

% --- CODE LISTING STYLE ---
\lstset{
    basicstyle=\ttfamily\small,
    keywordstyle=\color{janusblue}\bfseries,
    commentstyle=\color{gray}\itshape,
    stringstyle=\color{accentgold},
    backgroundcolor=\color{codegray},
    breaklines=true,
    frame=single,
    numbers=left,
    numberstyle=\tiny\color{gray},
    tabsize=4,
    showstringspaces=false
}

% --- HEADER & FOOTER ---
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\textcolor{janusblue}{\textbf{Project JANUS}}}
\fancyhead[R]{\textcolor{janusblue}{Complete Technical Documentation}}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0.5pt}
\renewcommand{\footrulewidth}{0pt}

% --- SECTION FORMATTING ---
\titleformat{\section}
    {\Large\bfseries\color{janusblue}}
    {\thesection}{1em}{}
\titleformat{\subsection}
    {\large\bfseries\color{janusblue}}
    {\thesubsection}{1em}{}
\titleformat{\subsubsection}
    {\normalsize\bfseries\color{janusblue}}
    {\thesubsubsection}{1em}{}

% =============================================================================
% DOCUMENT START
% =============================================================================
\begin{document}

% =============================================================================
% TITLE PAGE
% =============================================================================
\begin{titlepage}
    \pagenumbering{gobble}
    \centering
    \vspace*{2cm}

    {\Huge \textbf{Project JANUS}} \\[0.5cm]
    {\LARGE \textbf{Complete Technical Documentation}} \\[1cm]

    {\Large \textit{A Brain-Inspired Architecture for Autonomous Financial Systems}} \\[2.5cm]

    \begin{tcolorbox}[colback=gray!10, colframe=janusblue, width=0.9\textwidth, arc=3mm, boxrule=0.5mm]
        \centering
        \textbf{\large The Complete JANUS Suite}\\[0.5cm]

        \textbf{\textcolor{janusblue}{Volume I: Architecture Overview}}\\
        The philosophical foundation and system design\\[0.3cm]

        \textbf{\textcolor{forwardblue}{Volume II: Forward Service}}\\
        Real-time trading, pattern recognition, and execution\\[0.3cm]

        \textbf{\textcolor{backwardblue}{Volume III: Backward Service}}\\
        Memory consolidation, schema formation, and learning\\[0.3cm]

        \textbf{\textcolor{neurocolor}{Volume IV: Neuromorphic Architecture}}\\
        Brain-inspired components and cognitive mapping\\[0.3cm]

        \textbf{\textcolor{rustcolor}{Volume V: Rust Implementation}}\\
        Production-ready ML system with Rust and Python
    \end{tcolorbox}

    \vspace{1.5cm}

    \textbf{\Large Classification: Master Technical Document} \\[0.5cm]
    \textbf{\Large Version: 2.0 (Complete Edition)} \\[2cm]

    \textbf{Author:} Jordan Smith \\
    \textit{github.com/nuniesmith} \\[0.5cm]
    \textbf{Date:} \today

    \vfill

    \textit{``The god of beginnings and transitions, looking simultaneously to the future and the past.''}
\end{titlepage}

% =============================================================================
% TABLE OF CONTENTS
% =============================================================================
\newpage
\pagenumbering{roman}
\tableofcontents
\newpage
\pagenumbering{arabic}

% =============================================================================
% PREFACE
% =============================================================================
\section*{Preface: The Complete JANUS Documentation}
\addcontentsline{toc}{section}{Preface: The Complete JANUS Documentation}

This document represents the complete technical specification for \textbf{Project JANUS}, a neuromorphic trading intelligence system that bridges neuroscience, machine learning, and quantitative finance.

\subsection*{How to Read This Document}

This master document combines five interconnected volumes that can be read independently or as a unified whole:

\begin{enumerate}
    \item \textbf{Volume I - Architecture Overview (main.tex)}: Start here for the big picture. This volume explains the philosophical motivation, the dual-service architecture, and how all components fit together.

    \item \textbf{Volume II - Forward Service (forward.tex)}: Deep dive into the real-time trading engine. Read this for implementation details of visual pattern recognition (DiffGAF + ViViT), logical reasoning (Logic Tensor Networks), and the decision-making system.

    \item \textbf{Volume III - Backward Service (backward.tex)}: Explore the learning and memory system. This volume covers the three-timescale memory hierarchy, Sharp-Wave Ripple simulation, schema consolidation, and UMAP visualization.

    \item \textbf{Volume IV - Neuromorphic Architecture (neuro.tex)}: Understand the brain-inspired design philosophy. Maps each trading component to its neuroscience equivalent, from cortex to cerebellum.

    \item \textbf{Volume V - Rust Implementation (rust.tex)}: Production deployment guide. Details the Rust-first ML stack, FastAPI gateway, Docker/Kubernetes deployment, and migration roadmap.
\end{enumerate}

\subsection*{Document Structure}

Each volume maintains its independence while contributing to the unified vision. Cross-references are provided where concepts span multiple volumes. Implementation checklists at the end of each technical volume provide actionable development guidance.

\subsection*{Intended Audience}

\begin{itemize}
    \item \textbf{Quantitative Researchers}: Volumes I, II, and III
    \item \textbf{ML Engineers}: Volumes II, III, and V
    \item \textbf{System Architects}: Volumes I, IV, and V
    \item \textbf{Neuroscience-Curious}: Volumes I and IV
    \item \textbf{DevOps/Infrastructure}: Volume V
\end{itemize}

\vspace{1cm}
\noindent\textit{Welcome to the future of algorithmic trading.}

\newpage

% =============================================================================
% PART I: ARCHITECTURE OVERVIEW
% =============================================================================
\part{Architecture Overview}
\label{part:main}

\input{main}

\clearpage

% =============================================================================
% PART II: FORWARD SERVICE
% =============================================================================
\part{Forward Service: Real-Time Trading}
\label{part:forward}

\input{forward}

\clearpage

% =============================================================================
% PART III: BACKWARD SERVICE
% =============================================================================
\part{Backward Service: Memory \& Learning}
\label{part:backward}

\input{backward}

\clearpage

% =============================================================================
% PART IV: NEUROMORPHIC ARCHITECTURE
% =============================================================================
\part{Neuromorphic Architecture}
\label{part:neuro}

\input{neuro}

\clearpage

% =============================================================================
% PART V: RUST IMPLEMENTATION
% =============================================================================
\part{Rust Implementation Guide}
\label{part:rust}

\input{rust}

\clearpage

% =============================================================================
% UNIFIED REFERENCES
% =============================================================================
\section*{Unified References}
\addcontentsline{toc}{section}{Unified References}

\textit{Note: Each volume contains its own reference section. This unified section consolidates key references across all five volumes.}

\begin{itemize}[leftmargin=*, itemsep=0.3em]
    \item \textbf{Buzsáki, G.} (2015). \textit{The Brain from Inside Out}. Oxford University Press.
    \item \textbf{Hassabis, D., et al.} (2017). Neuroscience-inspired artificial intelligence. \textit{Neuron}, 95(2), 245-258.
    \item \textbf{Mnih, V., et al.} (2015). Human-level control through deep reinforcement learning. \textit{Nature}, 518(7540), 529-533.
    \item \textbf{Serrà, J., et al.} (2018). Image-based time series classification with gramian angular fields. \textit{arXiv:1506.00327}.
    \item \textbf{Arnab, A., et al.} (2021). ViViT: A video vision transformer. \textit{ICCV 2021}.
    \item \textbf{Badreddine, S., et al.} (2022). Logic tensor networks. \textit{Artificial Intelligence}, 303, 103649.
    \item \textbf{O'Neill, J., et al.} (2010). Play it again: reactivation of waking experience and memory. \textit{Trends in Neurosciences}, 33(5), 220-229.
    \item \textbf{McInnes, L., et al.} (2018). UMAP: Uniform Manifold Approximation and Projection. \textit{arXiv:1802.03426}.
    \item \textbf{Klabnik, S. \& Nichols, C.} (2023). \textit{The Rust Programming Language}. No Starch Press.
    \item \textbf{Paszke, A., et al.} (2019). PyTorch: An imperative style, high-performance deep learning library. \textit{NeurIPS 2019}.
    \item \textbf{Almgren, R. \& Chriss, N.} (2001). Optimal execution of portfolio transactions. \textit{Journal of Risk}, 3, 5-40.
    \item \textbf{Easley, D., et al.} (2012). Flow toxicity and liquidity in a high-frequency world. \textit{The Review of Financial Studies}, 25(5), 1457-1493.
\end{itemize}

% =============================================================================
% MASTER IMPLEMENTATION CHECKLIST
% =============================================================================
\newpage
\section*{Master Implementation Checklist}
\addcontentsline{toc}{section}{Master Implementation Checklist}

This consolidated checklist spans all five volumes and provides a complete roadmap for building Project JANUS from scratch.

\subsection*{Phase 1: Foundation (Weeks 1-4)}

\subsubsection*{Infrastructure Setup}
\begin{itemize}[label=$\square$]
    \item Initialize Git repository with proper .gitignore
    \item Set up Rust workspace with cargo workspaces
    \item Configure Docker development environment
    \item Establish Python virtual environment for training
    \item Deploy PostgreSQL for system state
    \item Deploy Redis for caching
    \item Deploy Qdrant vector database
    \item Set up monitoring stack (Prometheus + Grafana)
\end{itemize}

\subsubsection*{Shared Libraries (Rust)}
\begin{itemize}[label=$\square$]
    \item Create \texttt{janus-common} crate for shared types
    \item Implement market data structures (OHLCV, orderbook)
    \item Create configuration management (TOML/YAML)
    \item Build logging infrastructure with \texttt{tracing}
    \item Implement error handling with \texttt{thiserror}
\end{itemize}

\subsection*{Phase 2: Forward Service (Weeks 5-8)}

\subsubsection*{Core Components}
\begin{itemize}[label=$\square$]
    \item Implement DiffGAF transformation module
    \item Build GAF video generator with sliding windows
    \item Export ViViT model from PyTorch to ONNX
    \item Integrate ONNX Runtime for inference
    \item Implement Logic Tensor Networks constraint evaluator
    \item Build multimodal fusion layer (Gated Cross-Attention)
    \item Implement Basal Ganglia dual pathways (Go/NoGo)
    \item Build Cerebellar forward model
\end{itemize}

\subsubsection*{Service Architecture}
\begin{itemize}[label=$\square$]
    \item Create async Tokio service with Axum/Actix
    \item Implement WebSocket streaming for real-time data
    \item Build REST API for configuration and control
    \item Add circuit breakers and rate limiting
    \item Implement comprehensive metrics collection
\end{itemize}

\subsection*{Phase 3: Backward Service (Weeks 9-12)}

\subsubsection*{Memory System}
\begin{itemize}[label=$\square$]
    \item Implement hippocampal episodic buffer (ring buffer)
    \item Build prioritized experience replay with TD-error
    \item Create SWR simulation module
    \item Implement schema representation in Qdrant
    \item Build AlignedUMAP for schema detection
    \item Create Parametric UMAP for anomaly detection
\end{itemize}

\subsubsection*{Batch Processing}
\begin{itemize}[label=$\square$]
    \item Implement sleep cycle scheduling
    \item Build parallel batch processor with Rayon
    \item Create schema consolidation pipeline
    \item Implement periodic pruning jobs
    \item Add comprehensive logging and monitoring
\end{itemize}

\subsection*{Phase 4: Training Gateway (Weeks 13-14)}

\subsubsection*{Python Services}
\begin{itemize}[label=$\square$]
    \item Create FastAPI gateway service
    \item Implement model training endpoints
    \item Set up Celery for async job processing
    \item Build model versioning system
    \item Create ONNX export pipeline
    \item Implement model validation tests
\end{itemize}

\subsection*{Phase 5: Integration \& Testing (Weeks 15-16)}

\subsubsection*{End-to-End Testing}
\begin{itemize}[label=$\square$]
    \item Create synthetic market data generators
    \item Build integration test suite
    \item Implement backtesting framework
    \item Add performance benchmarking
    \item Create stress testing scenarios
    \item Validate wash sale compliance
    \item Test circuit breakers and kill switches
\end{itemize}

\subsection*{Phase 6: Deployment (Weeks 17-20)}

\subsubsection*{Production Infrastructure}
\begin{itemize}[label=$\square$]
    \item Create Docker images for all services
    \item Write Docker Compose for local deployment
    \item Create Kubernetes manifests
    \item Set up CI/CD pipeline (GitHub Actions)
    \item Configure production monitoring
    \item Implement alerting rules
    \item Create runbooks for operations
    \item Conduct security audit
    \item Perform regulatory compliance review
\end{itemize}

\subsection*{Phase 7: Optimization (Ongoing)}

\begin{itemize}[label=$\square$]
    \item Profile hot paths and optimize bottlenecks
    \item Migrate to pure Rust ML inference (Candle/Burn)
    \item Implement model quantization (INT8)
    \item Add GPU acceleration where beneficial
    \item Optimize Qdrant query patterns
    \item Fine-tune memory allocation strategies
    \item Implement adaptive learning rates
    \item Add continual learning capabilities
\end{itemize}

% =============================================================================
% END MATTER
% =============================================================================
\newpage
\section*{About the Author}
\addcontentsline{toc}{section}{About the Author}

\textbf{Jordan Smith} is a quantitative researcher and software engineer specializing in neuromorphic computing and algorithmic trading systems. With a background in both neuroscience and machine learning, Jordan bridges the gap between biological intelligence and artificial systems.

\vspace{0.5cm}
\noindent\textbf{Contact:}
\begin{itemize}[leftmargin=*]
    \item GitHub: \url{https://github.com/nuniesmith}
    \item Project Repository: \url{https://github.com/nuniesmith/project-janus}
\end{itemize}

\vspace{1cm}
\noindent\textit{This document represents years of research at the intersection of neuroscience, machine learning, and quantitative finance. May it serve as a foundation for the next generation of intelligent trading systems.}

\end{document}
